\documentclass[11pt,a4paper,roman]{moderncv}      
\usepackage[english]{babel}

\moderncvstyle{classic}                            
\moderncvcolor{green}                            

% character encoding
\usepackage[utf8]{inputenc}                     

% adjust the page margins
\usepackage[scale=0.80]{geometry}

% personal data
\name{Diogo}{Correia}


\phone[mobile]{+351915800676}               
\email{dv\_correia@hotmail.com}                             


\begin{document}

\recipient{To}{Whom it may concern at Signify}
\date{\today}
\opening{Hope this letter finds you well with a great sunny day,}
\closing{Best regards,}
\makelettertitle

I am writing in response to my application for the \emph{Software Engineer} position. After careful consideration, I believe that my skills and experience may be a strong contribution to your team's efforts.

During my time at university, I consistently sought to expand my knowledge beyond the confines of electronics and telecommunications engineering. As early as my second year, I began experimenting with expanding electronics projects, striving to refine them to meet what I would expect from a commercial product. This exploration sparked my interest in computing and distributed systems.

Motivated by this newfound passion, I made the decision to pursue further studies in Turin, Italy, to deepen my understanding. While there, I focused on machine learning, automotive information systems and software for IoT applications.

Since graduating, I have been actively involved in the development of software and solutions for real-time location systems (RTLS) and radio frequency identification (RFID). Over the course of two years, I have assumed significant responsibilities in driving the technical aspects of the product. As a result, I am currently serving as the technical product leader for our RTLS and RFID offerings.

In addition to my core responsibilities, I have taken the initiative to spearhead several efforts aimed at enhancing our company's technical excellence and fostering innovation. For instance, I initiated a partnership with the DevOps team leader, focusing on providing internal python tools and reference code to improve software quality and accelerate product development.

More recently, I have been leading a working group comprised of lead developers from various teams. Together, we tackle shared challenges in a collaborative manner, ultimately expediting product development across the entire company.

My unwavering commitment to achieving technical excellence is a driving force in my professional journey. I thrive in environments that nurture innovation, as I firmly believe that technical advancements can lead to groundbreaking solutions. Moreover, I possess a deep passion for maintaining high technical standards and delivering well-designed products, which I bring with me every day to work.

I hope this overview provides you with a clearer understanding of my qualifications and aspirations. I eagerly look forward to the opportunity to discuss how my skills align with Signify's goals. Thank you for considering my application.

\vspace{0.5cm}

\makeletterclosing

\end{document}
